\documentclass[11pt]{article}

%%% These are some packages that are useful
\usepackage{circuitikz} %used for circuit diagrams
\usepackage{lastpage} %allows us to determine how many total pages there are
\usepackage{amsfonts, lipsum}
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage{mdframed, titlesec, setspace,verbatim, multicol}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} %sets the margins
\usepackage[unicode]{hyperref} %enhanced references
\usepackage{tikz, pgfplots, xcolor}
\usepackage{fancyhdr} %creates a fancy header for labeling document/name/date 
\usepackage{listings}
\usepackage{xcolor}
\usepackage{vwcol}  
\usepackage{enumitem}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\parindent}{25pt}
\setlength{\textheight}{9in}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large PHY 482 - \textbf{Project Reflections}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}
\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

%%Use these commands to clear the fancyhdr settings and horizontal header line.
%\fancyhf{} % sets both header and footer to nothing
%\renewcommand{\headrulewidth}{0pt}

%%% Document Starts now
\begin{document} 

\begin{center}
	{\Large E \& M II - Project 2 Reflections.}
\end{center}

For week one, Eric created a Google Document in which we both went in and answered questions regarding our topic (questions given by the homework). We worked together and also found sources and ideas we may be able to use later. This information was combined in the "EMProject2\_original draft.pdf" file in the "Project Outline (week 2-3 assignment)" folder of our github. After receiving our feedback, we spend a long time trying to find a different (more E \& M related) topic we could possibly do our project on. We ended up sticking to what we originally decided of the Zeeman effect but tried to narrow it down further. We then discussed what we should do and together in a google document created the first part of the "Project Outline.pdf" document located in the same folder previously listed. 

This week (week 3), Eric is off looking at Graduate schools or something of that order. Because of this, I wrote up a addition to our "Project Outline" file title "explanation of the models and theoretical calculations" in accordance with the assignment this week. After which I also included an "Updated Project Timeline" included in the same file in order to attempt corrections from the previous feedback. I also have included a poster template from a previous project of mine we may be able to use for our final poster as well as uploaded some handwritten calculations of the energy level shifts in the hydrogen atom due to a uniform magnetic field (the zeeman effect). So far the total work is a little weighted towards me as of this week but I expect to throw a large amount of the computational modeling at Eric once I can finish the calculations so it should even out in the wash. I also plan on moving the currect calculations over into a \LaTeX document as soon as time permits with precise explanations of where everything comes from so we can better understand everything and see what we have.

Regarding our project specifically, we will still need to address the situation of what exactly we can model. It would be nice if we could come accross something unique to computationally model that we can not think of at the moment but at the moment we are planning to model the effect with varying magnetic field strengths but maintaining it as a uniform field in time. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















